\thetitle

### 2020-11-24 sun_phases/spin_qudit_tomo.tex
remove sub-section numbering in appendix

The reconstruction error bound in Eq.~\eqref{eq:bound} nominally provides a straightforward answer: at a fixed total number of measurements, $N=n\abs{V}$, the number of measurement axes should be chosen to minimize the (squared) reconstruction error $\E_V\p{\rho}^2<\epsilon_V^2/n\propto\epsilon_V^2\abs{V}$.
We therefore consider the measurement-adjusted error scale
\begin{align}
  \beta(p)
  \equiv \min\set{\epsilon_V:\abs{V}=2d-1+p} \times \sqrt{2d-1+p}
\end{align}
as a function of $p$, the number of measurement axes exceeding $2d-1$.
Though we cannot minimize over all suitable choices of measurement axes $V$ to compute $\beta(p)$, we can compute an empirical upper bound $\tilde\beta(p)\ge\beta(p)$ by minimizing over a large number of randomly chosen $V$.
Figure \ref{fig:axes} shows the results of such empirical minimization, where we find that $\tilde\beta(p)$ drops substantially before plateauing at $p\approx d$, after which there are only marginal benefits to using more measurement axes.
In the interest of reducing experimental complexity as well as the runtime of our tomography protocol, which grow linearly in $\abs{V}$, we therefore conclude that spin qudit tomography should be performed with $\abs{V}\approx3d$ measurement axes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comments on a tight reconstruction error bound}
\label{sec:tight}

>>>>

The reconstruction error bound in Eq.~\eqref{eq:bound} nominally provides a straightforward answer: at a fixed total number of measurements, $N=n\abs{V}$, the number of measurement axes should be chosen to minimize the (squared) reconstruction error $\E_V\p{\rho}^2<\epsilon_V^2/n\propto\epsilon_V^2\abs{V}$.
We therefore consider the measurement-adjusted error scale
\begin{align}
  \beta(p)
  \equiv \min\set{\epsilon_V:\abs{V}=2d-1+p} \times \sqrt{2d-1+p}
\end{align}
as a function of $p$, the number of measurement axes exceeding $2d-1$.
Though we cannot minimize over all suitable choices of measurement axes $V$ to compute $\beta(p)$, we can compute an empirical upper bound $\tilde\beta(p)\ge\beta(p)$ by minimizing over a large number of randomly chosen $V$.
Figure \ref{fig:axes} shows the results of such empirical minimization, where we find that $\tilde\beta(p)$ drops substantially before plateauing at $p\approx d$, after which there are only minor benefits to using more measurement axes.
In the interest of reducing experimental complexity as well as the runtime of our tomography protocol, which grow linearly in $\abs{V}$, we therefore conclude that spin qudit tomography should be performed with $\abs{V}\approx3d$ measurement axes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Comments on a tight reconstruction error bound}
